---
title: "Deep Drop Data"
author: "Brady Johnston"
date: "26/06/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r etup, message=FALSE}
library(tidyverse)
```


# Deep Drop Data

### Checking the csv
```{r}
df <- read.csv("data/4e2c_data_20210625_121022.csv")
df %>% 
  rename(time = 1, 
         temp = 2, 
         depth = 3) %>% 
  mutate(
    time = lubridate::as_datetime(time)
  ) %>% 
  filter(!is.na(temp)) %>% 
  mutate(
    direction = case_when(
      time >= lubridate::as_datetime("2021-06-25 13:28:23") ~ "up", 
      time < lubridate::as_datetime("2021-06-25 13:28:23") ~ "down"
    )
  ) %>% 
  group_by(direction) -> df

df  %>% 
  head() %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_minimal()
```


## Depth Over Time

```{r}
library(echarts4r)
chart1 <- df %>% 
  mutate(depth = -depth) %>% 
  e_charts(time, elementId = "chart1", height = 400) %>% 
  e_line(depth) %>% 
  e_legend(show = FALSE) %>% 
  e_tooltip(trigger = "axis") %>% 
  e_title("Sesnor Depth Over Time") %>% 
  e_axis_labels(x = "Time", y = "Depth (m)")

# chart1
```

## Temperature Over Time
```{r}
chart2 <- df %>% 
  e_charts(time, elementId = "chart2", height = 400) %>% 
  e_line(temp) %>% 
  e_legend(show = FALSE) %>% 
  e_tooltip(trigger = "axis") %>% 
  e_connect("chart1") %>% 
  e_title("Sensor Temperature Over Time") %>% 
  e_axis_labels(x = "Time", y = "Temperature (ºC)")

# chart2
```

## Connected Plots
```{r}
e_arrange(
  chart1,
  chart2
)
```


## Temperature vs Depth
```{r}
df %>% 
  
  e_charts(depth) %>% 
  # e_scatter(temp,) %>% 
  e_line(temp) %>% 
  e_tooltip(trigger = "axis") %>% 
  e_legend(show = TRUE) %>% 
  e_title("Temperature At Depth") %>% 
  e_axis_labels(x = "Depth (m)", y = "Temperature (ºc)")
```

# Estimating Line Shape

While the descent had some time points where there was a pause, the ascent stage
was consistent until the first nisken was recovered at ~ 50 m depth.

The winch operated at ~ 100 m / 2 minutes, or a speed of 50 m / min.

Just the ascent stage shows two distinct ascent  _pre_ and _post_ 13:40, or above and below ~250 m.

```{r}
df %>% 
  filter(
    direction == "up"
  ) %>% 
  mutate(depth = -depth) %>% 
  e_charts(time) %>% 
  e_line(depth)
```


During ascent, the winch was stopped for the top nisken bottle at a ~ 25 metres 
as 5 of them were spaced 5 metres apart.

The winch then pulled ~975 m of line in ~ 22 minutes, at a rate of ~ 44 m / minute.


```{r}
# lubridate::time_length(df$time[78] - df$time[79], unit = "minutes")

df %>% 
  mutate(
    line_in = lubridate::time_length(time - df$time[79], unit = "minutes"), 
    line_in = ifelse(
      line_in < 0, 
      NA, 
      line_in
    ), 
    line_out = line_in * 45 - 1000, 
    depth = -depth, 
    rate = depth - lag(depth), 
    # rate = rate / 45, 
    
    diff = depth - line_out
  ) %>% 
  ggplot(
    aes(diff, depth)
    ) + 
  # geom_path() +
  geom_point() + 
  coord_cartesian(
  ylim = c(-1000,0),
  xlim = c(0,1000)) +
  geom_hline(yintercept = -1000) + 
  geom_vline(xintercept = 0) + 
  theme(aspect.ratio = 1) + 
  labs(
    title = "Potential Shape of Line"
  )
  
```

